Atmospheric escape and star-planet-interaction in the HAT-P-67 b system

### 2023-02-07 paper/paper1/ms.tex
Switch to Modern format for the paper for now
Writing prose for the introduction

\documentclass[twocolumn]{aastex631}
\bibliographystyle{aasjournal}

@@

\authorcomment1{Todo: Intro topics-- atmospheric escape, variety of exoplanets, extremes, photoevaporation, Fulton Gap, Helium 10830 backgorund, etc...}

%Exoplanet atmospheres must exhibit an unimaginable dynamic range in physical and chemical properties, spanning familiar life-sustaining worlds to uninhabitable toxic wastelands.  Most systems exhibit signals too weak to register with current instruments, so our understanding of the variety of exoplanet atmospheres has been built on a foundation of comparative studies \citep{2016Natur.529...59S}, population studies \citep{2017AJ....154..109F}, and theoretical understanding.  Extreme atmospheres offer the benefit of being more conspicuous, while challenging the limits of the imagination and motivating new directions for building theory.

At least 8 systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.

>>>>

\documentclass[modern]{aastex631}
\bibliographystyle{aasjournal}

@@

Atmospheric escape appears to be a compulsory phase for exoplanets of a certain size and insolation, statistically imprinted in the dearth of 1.5-2.0~$R_\oplus$ planets in the California-Kepler survey \citep{2017AJ....154..109F}.  The two physical mechanisms for this fleeting interlude between mini-Neptunes and super-Earths include photoevaporation \citep{2013ApJ...775..105O,2017ApJ...847...29O} and core-powered mass loss \citep{2019MNRAS.487...24G}.  Whatever the cause, some large fraction of planets must undergo atmospheric escape and the signal should be widely discernable, at least in observationally favorable configurations.

The most amenable observing configuration involves transit spectroscopy in one of three key atomic transitions: Ly~$\alpha$, \ion{He}{1} 10833 \AA, or H~$\alpha$...

Enough uncertainty exists in the tradeoffs among physical mechanisms, system ages, and timescales to make it unclear whether any given exoplanet will be actively undergoing atmospheric escape.  The most favorable conditions may include certain commonalities: close-in, low surface gravity exoplanets with a strategically chosen radius range.  The 1.5-2.0 Earth radius range could be expected to harbor atmospheres that have not yet shed their gaseous envelopes, still in the act of descending to their final state.  Alternatively, inflated Hot Jupiters could be so dramatically ablated as to overcome the somewhat stronger potential well.  Significant gains in understanding can therefore be expected from observational studies sampling the extremes of the exoplanet distribution.

8 systems have Helium 10830 exosphere measurements to date: \object[GJ 3470]{GJ3470} \citep{2020ApJ...894...97N, 2021A&A...647A.129L}, \object{HD 63433 c} \citep{2022AJ....163...68Z}, WASP 107 b \citep{2019A&A...623A..58A,2020AJ....159..115K}, HD 209458 b \citep{2019A&A...629A.110A}, WASP 69 b \citep{2020AJ....159..278V}, WASP 52 b \citep{2020AJ....159..278V}, HD 189733 b \citep{2021A&A...647A.129L}, and HAT-P-18 b \citep{2021ApJ...909L..10P}.
